Rotations and Insecticide Resistance initial plots

### 2017-11-01 inst/documents/rotations_notes.Rmd
improve plot legends

@@

~ fix migration rate to be between 0 & 1, where 1 is random movement.

@@

~ improve plot legend to show when insecticide in use

>>>>

done ~ fix migration rate to be between 0 & 1, where 1 is random movement.

~ allowed plots not to show refuge

@@

~ improve plot legend to show when insecticide in use
~ do a few plots for Dave Malone
#high cost, no migration
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0.1 , logy = FALSE )
#no cost
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 10 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )
#no cost and rotate when resistant
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 0 , eff = 1 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration = 0 , cost = 0 , logy = FALSE )

@@
